\documentclass[../main.tex]{subfiles}

\begin{document}
    
\chapter*{BIBLIOGRAPHY}

\begin{multicols}{2}
    Anscombe, F. J., \textit{"Graphs in Statistical Analysis," Am. Stat.},
    27(1):17-21, 1973.

    Attaway, S., MATLAB: \textit{A Practical Introduction to Programming and Problem Solving}, Elsevier Science,
    Burlington, MA, 2009.

    Bogacki, P. and L. F. Shampine, "A 3(2) Pair of Runge-Kutta
    Formulas," \textit{Appl. Math. Letters}, 2(1989):1-9, 1989.

    Brent, R. P., \textit{Algorithms for Minimization Without
    Derivatives}, Prentice Hall, Englewood Cliffs, 
    NJ, 1973.

    Butcher, J. C., "On Runge-Kutta Processes of Higher
    Order," \textit{J. Austral. Math. Soc.}, 4:179, 1964.

    Carnahan, B., H. A. Luther, and J. O. Wilkes, \textit{Applied
    Numerical Methods}, Wiley, New York, 1969.

    Chapra, S. C. and R. P. Canale, \textit{Numerical Methods for
    Engineers}, 6th ed., McGraw-Hill, New York, 2010.

    Cooley, J. W. and J. W. Tukey, "An Algorithm for the
    Machine Calculation of Complex Fourier Series,"
    \textit{Math. Comput.}, 19:297-301, 1965.

    Dekker, T. J., "Finding a Zero by Means of Successive
    Linear Interpolation." In B. Dejon and P. Henrici
    (editors), \textit{Constructive Aspects of the Fundamental
    Theorem of Algebra}, Wiley-Interscience, New York,
    1969, pp. 37-48.

    Dormand, J. R. and P. J. Prince, "A Family of Embedded
    Runge-Kutta Formulae," \textit{J. Comp. Appl. Math.},
    6:19-26, 1980.

    Draper, N. R. and H. Smith, \textit{Applied Regression Analysis},
    2d ed., Wiley, New York, 1981.

    Fadeev, D. K. and V. N. Fadeeva, \textit{Computational Methods
    of Linear Algebra}, Freeman, San Francisco, 1963.

    Forsythe, G. E., M. A. Malcolm, and C. B. Moler, \textit{Computer Methods for Mathematical Computation},
    Prentice Hall, Englewood Cliffs, NJ, 1977.

    Gabel, R. A. and R. A. Roberts, \textit{Signals and Linear
    Systems}, Wiley, New York, 1987.

    Gander, W. and W. Gautschi, \textit{Adaptive Quadrature-
    Revisited}, BIT \textit{Num. Math.}, 40:84-101, 2000.

    Gerald, C. F. and P. O. Wheatley, \textit{Applied Numerical 
    Analysis}, 3d ed., Addison-Wesley, Reading, 
    MA, 1989.

    Hanselman, D. and B. Littlefield, \textit{Mastering} MATLAB 7,
    Prentice Hall, Upper Saddle River, NJ, 2005.

    Hayt, W. H. and J. E. Kemmerly, \textit{Engineering Circuit
    Analysis}, McGraw-Hill, New York, 1986.

    Heideman, M. T., D. H. Johnson, and C. S. Burrus, "Gauss
    and the History of the Fast Fourier Transform," \textit{IEEE
    ASSP Mag.}, 1(4):14-21, 1984.

    Hornbeck, R. W., \textit{Numerical Methods}, Quantum, 
    New York, 1975.

    James, M. L., G. M. Smith, and J. C. Wolford, \textit{Applied
    Numerical Methods for Digital Computations with
    FORTRAN and CSMP}, 3d ed., Harper \& Row, 
    New York, 1985.

    Moler, C. B., \textit{Numerical Computing with MATLAB}, SIAM,
    Philadelphia, 2004.

    Moore, H., \textit{MATLAB for Engineers}, 2nd ed., Prentice Hall,
    Upper Saddle River, NJ, 2008.

    Ortega, J. M., \textit{Numerical Analysis-A Second Course},
    Academic Press, New York, 1972.

    Palm, W. J. III, \textit{A Concise Introduction to MATLAB},
    McGraw-Hill, New York, 2007.

    Ralston, A., "Runge-Kutta Methods with Minimum Error
    Bounds," \textit{Match. Comp.}, 16:431, 1962.

    Ralston, A. and P. Rabinowitz, \textit{A First Course in Numerical
    Analysis}, 2d ed., McGraw-Hill, New York, 1978.

    Ramirez, R. W., \textit{The FFT, Fundamentals and Concepts},
    Prentice Hall, Englewood Cliffs, NJ, 1985.

    Recktenwald, G., \textit{Numerical Methods with MATLAB},
    Prentice Hall, Englewood Cliffs, NJ, 2000.

    Scarborough, I. B., \textit{Numerical Mathematical Analysis}, 
    6th ed., Johns Hopkins Press, Baltimore, MD, 1966.

    Shampine, L. F., \textit{Numerical Solution of Ordinary Differential
    Equations}, Chapman \& Hall, New York, 1994.

    Van Valkenburg, M. E., \textit{Network Analysis}, Prentice Hall,
    Englewood Cliffs, NJ, 1974.

    White, F. M., \textit{Fluid Mechanics}. McGraw-Hill, New York,
    1999.
    
\end{multicols}
\end{document}